Sparse Function Space Representation of Neural Networks for Exploration and Retention

### 2023-05-10 paper/main.tex
update cl results table

Sparse Gaussian processes \citep{hensman2013gaussian} are a principled way to scale Gaussian processes to large datasets by changing the complexity from $O(n^3)$ to $O(m^3)$ with $m$ the number of inducing points, and typically $m \ll n$. The key insight is to use a sparse approximating distribution $q(\vu; \vm, \MV)$, where $\vm \in \R^{m}$ and $\MV \in \R^{m \times m}$, and find its parameters through maximizing the evidence lower bound (ELBO). The distribution at all over points is then defined as $q_{\vu}(f) = \int p(f \mid \vu) q(\vu) d\vu$. The dual parameterization \cite{adam2021dual} states that we can decompose the optimal sparse Gaussian process posterior as follows:
\begin{equation}
   \myexpect_{q_{\vu}(f)}[f_i] = \vkzs^{\T} \valpha , \quad 
   \textrm{Var}_{q_{\vu}(f)}[f_i]  = \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \vbeta)^{-1} ]\vkzs.
\end{equation}

Here, we omit the dependency of the kernel on $n$, and simply use $\MKxx$ to denote the $n \times n$ matrix with $\kappa(\vx_i,\vx_j)$ as the $ij$\textsuperscript{th} entry, computed for all $\vx_i \in\vX$ where $\vX = (\vx_1,\ldots,\vx_n)$. Similarly, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.

The dual parameters consist of an $m$-length vector $\valpha$ and $m\times m$-size matrix $\vbeta$, defined as
\begin{equation} 
   \vlambda = [ \MKzz + \vbeta]\valpha  = \sum_{i \in \mathcal{D}_{n}}  \vkzi \, \tilde{\lambda}_{i}, \quad
   \vbeta = \sum_{i \in \mathcal{D}_{n}} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,
\label{eq:dual_sparse}
\end{equation}

where $\tilde{\lambda}_i = \alpha_i - \myexpect_{q_{\vu}(f)}[f_i] \hat{\beta}_i$ with $(\hat{\alpha}_i, \hat{\beta}_i)$ defined as,
\begin{equation}
 \alpha_i = \myexpect_{q_{\vu}(f_i)} [\nabla_{f_i}\log p(y_i \mid f_i)], \quad
   \beta_i = \myexpect_{q_{\vu}(f_i)} [ -\nabla^{2}_{f_i}\log p(y_i \mid f_i)],
\label{eq:svgp_dual}
\end{equation}

@@

\begin{table}[t!] 
  \centering\scriptsize
  \caption{TODO: CL Experiments. $^*$ Methods relying only on weight regularization. \color{blue}{Results from \cite{rudner2022continual}.} \color{red}{Preliminary results need more runs or hyperparam tuning}}
	\label{tbl:cl_table_1}
	% Control table spacing
	\renewcommand{\arraystretch}{1.}
	\setlength{\tabcolsep}{2pt}
	\setlength{\tblw}{0.14\textwidth}

@@

\section{Experiment details}

\subsection{UCI}

\begin{table}[t!] 
  \centering\scriptsize
  \caption{Negative log predictive density (NLPD) (lower better) for the proposed model TODO} 
	\label{tbl:uci_all}
	% Control table spacing
	\renewcommand{\arraystretch}{1.}
	\setlength{\tabcolsep}{2pt}
	\setlength{\tblw}{0.14\textwidth}

    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
	\input{tables/uci_all.tex}
\end{table}

>>>>

Sparse Gaussian processes \citep{hensman2013gaussian} are a principled way to scale Gaussian processes to large datasets by changing the complexity from $O(n^3)$ to $O(m^3)$ with $m$ the number of inducing points, and typically $m \ll n$. The key insight is to use a sparse approximating distribution $q(\vu; \vm, \MV)$, where $\vm \in \R^{m}$ and $\MV \in \R^{m \times m}$, and find its parameters through maximizing the evidence lower bound (ELBO). The distribution at all over points is then defined as $q_{\vu}(f) = \int p(f \mid \vu) q(\vu) d\vu$. The dual parameterization \citet{adam2021dual} states that we can decompose the optimal sparse Gaussian process posterior as follows:
\begin{equation}
   \myexpect_{q_{\vu}(f)}[f_i] = \vkzs^{\T} \valpha , \quad 
   \textrm{Var}_{q_{\vu}(f)}[f_i]  = \kappa_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \vbeta)^{-1} ]\vkzs.
\end{equation}
The dual parameters consist of an $m$-length vector $\valpha$ and $m\times m$-size matrix $\vbeta$, defined as
\begin{equation} 
   \vlambda = [ \MKzz + \vbeta]\valpha  = \sum_{i \in \mathcal{D}_{n}}  \vkzi \, \tilde{\lambda}_{i}, \quad
   \vbeta = \sum_{i \in \mathcal{D}_{n}} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,
\label{eq:dual_sparse}
\end{equation}

where $\tilde{\lambda}_i = \alpha_i - \myexpect_{q_{\vu}(f)}[f_i] \beta_i$ with $(\hat{\alpha}_i, \hat{\beta}_i)$ defined as follows,
\begin{equation}
 \alpha_i = \myexpect_{q_{\vu}(f_i)} [\nabla_{f_i}\log p(y_i \mid f_i)], \quad
   \beta_i = \myexpect_{q_{\vu}(f_i)} [ -\nabla^{2}_{f_i}\log p(y_i \mid f_i)],
\label{eq:svgp_dual}
\end{equation}

@@

\begin{table}[t!] 
  \centering\scriptsize
  \caption{
  TODO: CL Experiments. $^*$ Methods relying only on weight regularization. 
  \color{blue}{Results from \cite{rudner2022continual}.} 
  %\color{red}{Preliminary results need more runs or hyperparam tuning}
  }
	\label{tbl:cl_table_1}
	% Control table spacing
	\renewcommand{\arraystretch}{1.}
	\setlength{\tabcolsep}{2pt}
	\setlength{\tblw}{0.14\textwidth}

@@
